Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-04 text/ms.tex
Tweak text to work with thesis

\bibliographystyle{apalike}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}

@@

\caption[Estimates of population dynamics heavy-tailedness for \nuCoefPopN\
  populations of birds, mammals, insects, and fishes.]{Estimates of population dynamics heavy-tailedness for \nuCoefPopN\
  populations of birds, mammals, insects, and fishes. Small values of $\nu$
  ($\lesssim 10$) suggest heavy-tailed black-swan dynamics; larger values of
  $\nu$ suggest approximately normal-tailed dynamics. Vertical points and line
  segments represent posterior medians and 50\% / 90\% credible intervals for
  individual populations. Inset plots show probability that $\nu < 10$
  (probability of heavy tails) for populations arranged by taxonomic order and
  sorted by decreasing mean Pr($\nu < 10$). Taxonomic orders with three or
  fewer populations in panel a are omitted for space. Red to yellow points
  highlight populations with a high to moderately high probability of
  heavy-tailed black-swan dynamics.}

>>>>

\renewcommand{\baselinestretch}{\tighttextstretch}
\normalsize
\bibliographystyle{apalike}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}

\clearpage
\renewcommand{\baselinestretch}{\textstretch}
\normalsize

@@

\caption[Estimates of population dynamics heavy-tailedness for \nuCoefPopN\
  populations of birds, mammals, insects, and fishes.]{Estimates of population dynamics heavy-tailedness for \nuCoefPopN\
  populations of birds, mammals, insects, and fishes. Small values of $\nu$
  approximately ($< 10$) suggest heavy-tailed black-swan dynamics; larger values of
  $\nu$ suggest approximately normal-tailed dynamics. Vertical points and line
  segments represent posterior medians and 50\% / 90\% credible intervals for
  individual populations. Inset plots show probability that $\nu < 10$
  (probability of heavy tails) for populations arranged by taxonomic order and
  sorted by decreasing mean Pr($\nu < 10$). Taxonomic orders with three or
  fewer populations in panel a are omitted for space. Red to yellow points
  highlight populations with a high to moderately high probability of
  heavy-tailed black-swan dynamics.}
